---
title: Hello World
title-block-banner: true
affiliation-title: affiliation-title	
abstract-title: abstract-title	
description-title: description-title	
published-title: published-title	
author: "Jonny Hou "
date: "Report Last Run: `r Sys.time()`"
execute:
  cache: true
format: 
  html:
    code-fold: true
    toc: true
  pdf:
    keep-tex: true
    include-in-header:
      - text: |
          \usepackage{ standalone }
    toc: true
    lof: true
    lot: true
---

# Hello World

This is some python code, in which we define a function `hello`:

```{python} 
def hello():
  print("Hello")
```

```bash
git clone
```

This is how we call it:

```{python} 
hello()
```

```haskell
xs = [x | x <- [1..10]]
```

We can press `gd` to go to its definition.

Let's demonstrate the autocompletion:

```{python} 
import numpy as np
```

And code hovers with `K`.

# Furthermore

And then we can work on integrating this for multiple 
languages in the same document, like this R function:

```{r} 
hello_from_r <- function() {
  print("hello")
}
```

Unsurprisingly, the function does the same thing:

```{r} 
hello_from_r()
```


```{r}
library(tidyverse)
```


For a demonstration of a line plot on a polar axis, see @fig-polar.

```{python}
#| label: fig-polar
#| fig-cap: "A line plot on a polar axis"

import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(
  subplot_kw = {'projection': 'polar'} 
)
ax.plot(theta, r);
ax.set_rticks([0.5, 1, 1.5, 2]);
ax.grid(True);
plt.show
```

## Subcaptions
```{python}
#| label: fig-charts
#| fig-cap: "Charts"
#| fig-subcap: 
#|   - "First"
#|   - "Second"
#| layout-ncol: 2

import matplotlib.pyplot as plt
plt.plot([1,23,2,4])
plt.show()

plt.plot([8,65,23,90])
plt.show()
```

## Images
### Tikz/PGF Graphics
Seems could not show the imported tex directly as figure but as code when import. 
![test imported tex](tex/figure1.tex)

### Another way to do: tikz code block via raw LaTeX -> only works for PDF?

#### Raw Latex 

```{latex}
\begin{tabular}{|l|l|}\hline
Age & Frequency \\ \hline
18--25  & 15 \\
26--35  & 33 \\
36--45  & 22 \\ \hline
\end{tabular}
```

#### Raw latex with tikzpicture, doesn't work either
```{=latex}

\begin{tikzpicture}[{every node/.append style}=draw]
  \node [rectangle] (pop) at (0, 4) {Population};
  \node [ellipse] (y1) at (-5, 2.5) {$y_1$};
  \node [ellipse] (y2) at (-3, 2.5) {$y_2$};
  \node [ellipse] (y3) at (-1, 2.5) {$y_3$};
  \node [ellipse] (y4) at (1, 2.5) {$y_4$};
  \node [ellipse, draw=white] (ydots) at (3, 2.5) {$\dots$};
  \node [ellipse] (yn) at (5, 2.5) {$y_n$};

  \draw [-latex] (pop) to (y1);
  \draw [-latex] (pop) to (y2);
  \draw [-latex] (pop) to (y3);
  \draw [-latex] (pop) to (y4);
  \draw [-latex, dashed] (pop) to (ydots);
  \draw [-latex] (pop) to (yn);
\end{tikzpicture}

```

### Another way to do: strange font
Another one 
```{tikz, fig.cap = "Funk tikz", fig.ext = 'png'}
#| echo: false
#| fig-cap: "Complete pooling"
#| fig-align: center
#| fig-ext: png
#| out-width: 100%
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.geometric}
\begin{tikzpicture}[{every node/.append style}=draw]
  \node [rectangle] (pop) at (0, 4) {Population};
  \node [ellipse] (y1) at (-5, 2.5) {$y_1$};
  \node [ellipse] (y2) at (-3, 2.5) {$y_2$};
  \node [ellipse] (y3) at (-1, 2.5) {$y_3$};
  \node [ellipse] (y4) at (1, 2.5) {$y_4$};
  \node [ellipse, draw=white] (ydots) at (3, 2.5) {$\dots$};
  \node [ellipse] (yn) at (5, 2.5) {$y_n$};

  \draw [-latex] (pop) to (y1);
  \draw [-latex] (pop) to (y2);
  \draw [-latex] (pop) to (y3);
  \draw [-latex] (pop) to (y4);
  \draw [-latex, dashed] (pop) to (ydots);
  \draw [-latex] (pop) to (yn);
\end{tikzpicture}
```

### Ref way, in html works
Here's an empty DAG

```{tikz, echo=FALSE, cache=TRUE, fig.cap="Empty DAG", fig.align="center"}
\usetikzlibrary{positioning}
\begin{tikzpicture}[every node/.append style={draw, minimum size=0.5cm}]
\node [circle] (X) at (0,0) {};
\node [circle] (Y) at (2,0) {};
\node [rectangle] (Z) at (1,1) {};
\path [-latex] (X) edge (Y);
\draw [-latex] (Z) edge (Y);
\draw [-latex] (Z) edge (X);
\end{tikzpicture}
```
## Test r, tikz engine code block figure
<!-- ```{r setup} -->
<!-- options(tinytex.engine = "lualatex") -->
<!-- ``` -->

Where is the picture?
```{r, engine = 'tikz'}
#| label: fig-my-figure
#| echo: false
#| fig-align: center
#| fig-cap: "Some Caption"

\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.pathreplacing}

\begin{tikzpicture}
\draw (0,0)node(a){} -- (10,0) node (b) {} ;
\foreach \x in  {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10} % edit here for the vertical lines
\draw[shift={(\x,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
\foreach \x in {0, 0.2, 0.4, 0.6, 0.8, 1} % edit here for the numbers
\draw[shift={(\x*10,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below]
{$\x$};
\node at (8, 0.5) (eq1) {$\textcolor{red}{\boldsymbol{SQ}}$};
\node at (4, 0.5) (eq2) {$\textcolor{purple}{\boldsymbol{G_i(0)}}$}; 
\node at (7, 0.5) (eq2) {$\textcolor{purple}{\boldsymbol{G_i(1)}}$}; 
\node at (3, 0.5) (eq3) {$\textcolor{blue}{\boldsymbol{P}}$};
\node at (0, 0.5) (eq4) {$\textcolor{black}{\boldsymbol{x_i}}$};
\draw[decorate, decoration={brace, amplitude=6pt, mirror},] ([yshift=0.5cm]4,0.5)-- node[above=0.25cm]
{\shortstack{Text}}([yshift=0.5cm]3,0.5);
\draw[decorate, decoration={brace, amplitude=6pt},] ([yshift=-1cm]7,0)-- node[below=0.25cm]
{\shortstack{Text}}([yshift=-1cm]3,0);
\end{tikzpicture}
```
Finished

### way 1: in html works
Here is a TikZ picture

```{r, engine = 'tikz'}
\begin{tikzpicture}
 \draw (0,0) circle (1cm);
 %\pause
 \draw (0,0) circle (3cm);
\end{tikzpicture}
```

### way2: TikZ picture in html works

Here is a TikZ picture

```{tikz, fig.cap = "Funky tikz", fig.ext = 'png'}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\definecolor{zzffzz}{rgb}{0.6,1,0.6}
\definecolor{ffcctt}{rgb}{1,0.8,0.2}
\definecolor{yqyqdz}{rgb}{0.5019607843137255,0.5019607843137255,0.8509803921568627}
\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
\clip(-4.505289256198347,-6.316528925619829) rectangle (21.02198347107439,13.083471074380155);
\draw [line width=2pt,pattern color=yqyqdz,fill=yqyqdz,fill opacity=0.25] (2,0) circle (3cm);
\draw [line width=2pt,pattern color=ffcctt,fill=ffcctt,fill opacity=0.25] (6,0) circle (3cm);
\draw [line width=2pt,pattern color=zzffzz,fill=zzffzz,fill opacity=0.25] (4,3.46415) circle (3cm);
\end{tikzpicture}
```


### Roadmap with tikz

https://tex.stackexchange.com/questions/159835/milestone-graphic-in-tikz

https://github.com/cfiandra/timeline?tab=readme-ov-file

https://github.com/foretspaisibles/blueprint


```{tikz, fig.cap = "Funky tikz", fig.ext = 'png'}
\begin{tikzpicture}[
  every path/.style = {
   ->,
   > = stealth, 
   rounded corners},
  state/.style = {
    fill = white,
    text centered
  },
  node distance=1.25cm]

  \definecolor{color1}{HTML}{E7AD00}
  \definecolor{color2}{HTML}{A5CC19}
  \definecolor{color3}{HTML}{33B29A}
  \definecolor{color4}{HTML}{3380FF}
  \definecolor{color5}{HTML}{9033FF}
  \definecolor{color6}{HTML}{E5003D}

\begin{scope}[
  opacity = 1,
  fill opacity = 0.25,
  text opacity = 1,
  text width = 6em,
  text centered]

  \def\firstcircle{(90:2.75cm) circle (3.5cm)}
  \def\secondcircle{(210:2.75cm) circle (3.5cm)}
  \def\thirdcircle{(330:2.75cm) circle (3.5cm)}
  \draw [fill = color6] \firstcircle
    node [above = 10em] {Conhecimento de neg{\' o}cios};
  \draw [fill = color4] \secondcircle
    node [below left = 10em] {Matem{\' a}tica \& Estat{\' i}stica};
  \draw [fill = color2] \thirdcircle
    node [below right = 10em] {Computa{\c c}{\~a}o};

\end{scope}

\begin{scope}

  \node[state] (intuir) at (90:4.5) {Intuir};
  \node[state] (formular) at (60:3.5) {Formular};
  \node[state] (desenhar) at (30:2) {Desenhar};
  \node[state] (coletar)  at (-10:4)  {Coletar};
  \node[state] (armazenar) at (-30:5) {Armazenar};
  \node[state] (importar) at (-55:4.5) {Importar};
  \node[state] (manipular) at (-70:2.75) {Arrumar};
  \node[state] (transformar) at (-90:1.5) {Transformar};
  \node[state] (visualizar) at (-140:4.5) {Visualizar};
  \node[state] (modelar) at (-170:4) {Modelar};
  \node[state] (comunicar) at (150:2) {Compreender};
  \node[state] (agir) at (120:3.5) {Agir};

  \path[draw] (formular) edge[out=-90, in=90] (desenhar);
  \path[draw] (desenhar) edge[out=-90, in=90] (coletar);
  \path[draw] (coletar) edge[out=-70, in=90] (armazenar);
  \path[draw] (armazenar) edge[out=-90, in=0] (importar);
  \path[draw] (importar) edge[out=180, in=-90] (manipular);
  \path[draw] (manipular) edge[out=90, in=-90] (transformar);
  \path[draw] (transformar) edge[out=-120, in=0] (visualizar);
  \path[draw] (visualizar) edge[out=160, in=210] (modelar);
  \path[draw] (modelar) edge[out=0, in=140] (transformar);
  \path[draw] (modelar) edge[out=90, in=-90] (comunicar);
  \path[draw] (comunicar) edge[out=90, in=-90] (agir);
  \path[draw] (agir) edge[out=90, in=180] (intuir);
  \path[draw] (intuir) edge[out=0, in=90] (formular);

\end{scope}

\end{tikzpicture}
```

### flow
```{tikz, fig.cap = "Funky tikz", fig.ext = 'png'}
\begin{tikzpicture}
    \filldraw[red, thick] (0, 0) rectangle (2, 2);
\end{tikzpicture}


```
### circuitikz, by directly using tikz codeblock
<!-- ```{r, eval = TRUE, engine = 'tikz', engine.opts = list (template ="overview-header.tex") } -->
```{tikz, engine.opts=list(extra.preamble=c("\\usepackage{xcolor}", "\\usepackage{circuitikz}"))}

\begin{circuitikz}[american, voltage shift=0.5, scale=3] 
    \draw 
        (0,0) node[dinantenna] (ant) {} to[amp, l=LNA] ++(3, 0)
        to[bandpass, l=BPF, >] ++(1,0)
        to[short] ++(1,0) node[mixer, anchor=west] (mix) {Mixer}
        (mix.e) to[short, -o] ++(1, 0)
        (mix.w) node[inputarrow] {}
        (mix.s) node[inputarrow, rotate=90]{} -- ++(0,-0.5) node[oscillator, anchor=north, label={[anchor=north]below:LO}] {};

        \node[waves, scale=0.5, xshift=-2cm] at (0, 0.75) {};
\end{circuitikz}
```

Fix the canvas empty by removing scale, doesn't work.
export as svg, not by default pdf works! though font is bit strange...
```{tikz, engine.opts=list(extra.preamble=c("\\usepackage{xcolor}", "\\usepackage{circuitikz}"))}
#| echo: false
#| fig.align: center
#| fig.ext: svg
\begin{circuitikz}[american, voltage shift=0.5, scale=3] 
\draw (0,0) to[isource, l=$I_0$, v=$V_0$] (0,3) to[short, -*, i=$I_0$] (2,3) to[R=$R_1$, i>_=$i_1$] (2,0) -- (0,0); 
\draw (2,3) -- (4,3) to[R=$R_2$, i>_=$i_2$] (4,0) to[short, -*] (2,0); \end{circuitikz} 
```

### standalone

# Quarto Cheat Sheet

This section provides a quick reference for some of the most common and useful features in Quarto.

## Equations

You can write LaTeX equations inline like this: $\alpha+\beta=\gamma$. For block-level equations, use `$`:

$$
\int_0^\infty e^{-x^2} dx = \frac{\sqrt{\pi}}{2}
$$

You can give it a label for cross-referencing, like this one for the famous Euler's identity (@eq-euler).

$$
e^{i\pi} + 1 = 0
$$ {#eq-euler}

## Callouts

Callout blocks are useful for highlighting important information.

::: {.callout-note}
This is a note. It's useful for providing additional information.
:::

::: {.callout-warning}
This is a warning. Use it to alert readers to potential pitfalls.
:::

::: {.callout-tip}
This is a tip. It can provide a helpful piece of advice.
:::

## Tabsets

You can use tabsets to show different pieces of content in a single space.

::: {.panel-tabset}
### Python

@eq-euler

### R

``` {r}
fizz_buzz <- function(fbnums = 1:50) {
  output <- dplyr::case_when(
    fbnums %% 15 == 0 ~ "FizzBuzz",
    fbnums %% 3 == 0 ~ "Fizz",
    fbnums %% 5 == 0 ~ "Buzz",
    TRUE ~ as.character(fbnums)
  )
  print(output)
}
```
:::

## Cross-references

We already saw how to reference an equation with `@eq-euler`. You can also reference figures, like the polar plot we created earlier: @fig-polar.

To reference a section, you need to give it an ID like this: `## My Section {#sec-my-section}`. Then you can link to it using `[@sec-my-section]`.

# FAQ

0. for using tikz lib, seems extremely important to add code block like this in the first begining.

```{r}
library(tidyverse)
```

1. "! LaTeX Error: Can be used only in preamble."

    Asnswer: 
    - In the yaml header , adding the packages needed. 
    - For html case, seems remove header doesn't impact, as long as has tikz figure extrapreamble usepackage section.


2. r with tikz engine(by using knir?) seems most realiable way to include tikz picture

3. how to using latex standalone package for reuseable components?  Test with standalone tikz figure and parameterize it.

    Now finally, by using the knivr package refer the template config to use standalone package to parameterize the input for drawing diagrams.
    By defined template, it could define extra things and tikz picture, and there is other way to use preamble packages.
    {r, eval = TRUE, engine = 'tikz', engine.opts = list (template ="overview-header.tex") }

4. With tikz engine latex, with extra preamble
 
    {tikz, engine.opts=list(extra.preamble=c("\\usepackage{xcolor}", "\\usepackage{circuitikz}"))}

5. how to caching figures or computations:

    [quarto tutorial](https://quarto.org/docs/get-started/computations/rstudio.html#caching)
    You can use the cache option either at the document level using the YAML execute option.
    execute:
      cache: true
    However caching all code chunks in a document may not be preferable. You can also indicate which chunks should be cached directly with using a chunk option.
    #| cache: true
6. there might be python/r mix problem

7. font with svg in tikz, refer below to [fix](https://www.andrewheiss.com/blog/2021/08/27/tikz-knitr-html-svg-fun/)
